---
title: "Some Git/GitHub Basics"

output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(flair)
library(palmerpenguins)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
style_duo(
  primary_color = "#26116c",
  secondary_color = "#fd5e53",
  title_slide_text_color = "#fff8e7",
  header_font_google = google_font("Roboto"),
  text_font_google   = google_font("Roboto Condensed"),
  code_font_google   = google_font("Droid Mono")
)
```

# The Basics of Git/GitHub

* This is actually a pretty advanced system that's super awesome, but...

--

* You can get **REALLY** far on relatively little!

* What have we done so far:

--

1. Created a new repo.
2. **Cloned** a repo to our personal machine.
3. **Committed** and **pushed** local changes to our GitHub repo

Let's define these terms and a couple others...


---

# Basic Git Terms

1. **Clone**: A clone is a copy of a repository or the action of copying a repository. Often we will clone a repository on GitHub to our personal machine.

2. **Fork**: Creates a copy of a repository. Often we will fork someone else's GitHub repository to create our own GitHub copy of it.

3. **Pull**: If someone has changed code on a separate branch of a project and wants it to be reviewed to add to the master branch, that someone can put in a pull request. A **pull** happens when adding the changes to the master branch. **You should very often start your work sessions off by pulling your repo contents to make sure you're working with the most up-to-date files**.

4. **Commit**: A commit functions like a snapshot of all the files in the repo, at a specific moment (under the hood, things work a little differently though). Every time you make a commit you must also write a short **commit message**. You should generally be committing often so that these messages are short and specific to a single change (or very small amounts of changes).

5. **Push**: Update a remote branch with the commits made to the current branch. You're literally "pushing" changes onto the remote (GitHub usually) repository. A push can contain multiple commits. So, commit often, but push only usually a couple times per day (maybe even once).

---

# Activity: Create Your Own Copy of the Workshop Repo

1. Fork my repository for the workshop materials: [https://github.com/hglanz/GitHubInR_2021](https://github.com/hglanz/GitHubInR_2021)

2. Navigate to your own GitHub repository which is the copy of this repo.

3. Click the green "Code" button to clone the repo, but this time select "Download ZIP".

4. Extract/unzip the download to your desktop and open the R project file within (GitHubInR_2021.Rproj)

5. Within RStudio, make a change to the README: "This is my copy of the workshop materials!"

6. Save your changes, commit the changes, and then push the changes.

7. Verify your changes made it to your GitHub repo.

--

.center[
**What happened? What did we just do?!**
]