---
title: "Git for Collaboration"

output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(flair)
library(ISLR)
library(janitor)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
style_duo(
  primary_color = "#26116c",
  secondary_color = "#fd5e53",
  title_slide_text_color = "#fff8e7",
  header_font_google = google_font("Roboto"),
  text_font_google   = google_font("Roboto Condensed"),
  code_font_google   = google_font("Droid Mono")
)
```

class: center, middle, inverse

# Are We Collaborating Yet?!

---

# GitHub and Repo Workflow

1. Sit down at your computer with your favorite beverage.
2. Open the R Project file of the project you're about to work on.
3. Pull from the GitHub repo of the project you're about to work on.
3. Work...Commit...Work...Commit...
4. Push.
5. Work...Commit...Work...Commit...
6. Push.
7. Repeat more?
8. Give yourself a gold star and call it a day!

--

.center[
**So far this has been applied to and worked well for your OWN (solo) repo**
]

---

## Forking and Pull-Requesting is Not Necessarily What You Want

* Collaboration could take place by you forking the project repo; making changes to your own repo; pull-requesting the original/master repo in an attempt to merge your changes in.

--

* This can be good if you have "lots" of contributors or want tight control of work and changes.

--

* I have a lot of projects and teammates that I just trust, and so want us all to have master-push authority.

So...

--

1. Navigate back to your first repo of the workshop on GitHub.
2. Click the "Settings" tab at the top of the repo.
3. Click "Manage Access" on the left.
4. Let's talk about **GitHub collaborators** and some of the other GitHub bells and whistles!

---

# Activity: Working Together on a Repo

1. Put your GitHub username in the chat (or direct message me with it)
2. I am going to invite you to be a collaborator on the GitHubInR_2021_TeamRepo repo [https://github.com/hglanz/GitHubInR_2021_TeamRepo](https://github.com/hglanz/GitHubInR_2021_TeamRepo)
3. Accept the invitation.
4. Navigate to the repo page on GitHub and clone the repo to your personal machine using the ZIP approach as before.
5. Open the R Project file.
6. Create a new text document whose file name is your favorite movie followed by your age.
7. This file should contain a single line of text, your favorite quote in that movie.
8. Save that file.
9. Commit and push your changes.
10. Let's see everyone's files on the GitHub repo!

---

# GitHub Desktop

* RStudio has a wonderful interface for all of this Git stuff, but these two tools don't have to be linked!

* GitHub Desktop is a fantastic, light-weight application that also faciliates your Git and GitHub workflow (you can also use the command line for everything, if you prefer).

.center[
**GitHub Desktop Demo**
]


